The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-12-01 smurf_paper.tex
add power spectra and principal component analysis plots
detailed captions for PSD and PCA figures

\begin{figure}
\centering
\includegraphics[width=\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$25\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source.}
\label{fig:bolos_mix}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$25\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source. The grey signals overplotted in the top-two panels show the
  residual time-series after removing the common-mode signal. This
  operation shows: (i) that most of the low-frequency signal is common
  to all of the bolometers; and (ii) the non-correlated, and
  predominantly white noise at 450\,\micron\ is significantly larger
  than at 850\,\micron.}
\label{fig:bolos_mix}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{pspec.pdf}
\caption{Bolometer power spectral densities. Four representative
  bolometers have been selected from each sub-array, and the
  flat-fielded (but otherwise raw) PSDs are shown as coloured dotted
  lines (the blue signals are for the same time series as those shown
  in Fig.~\ref{fig:bolos_mix}). Horizontal dotted lines at $5 \times
  10^{-8}$ and $5 \times 10^{-9}$\,pW\,Hz$^{-1}$ at 450 and
  850\,\micron\ respectively, give the approximate white-noise
  levels. There are broad line features in the PSDs at both
  wavelengths above $\sim$35\,Hz. From $\sim$50\,Hz up to the Nyquist
  frequency, the gradual roll-off of the anti-aliasing filter is also
  evident.  At lower frequencies, the bolometer signals exhibit clear
  $1/f$ knees at approximately 2 and 4\,Hz at 450 and
  850\,\micron. The solid black lines are the PSDs of the common-mode
  signals at each wavelength, and the solid coloured lines show the
  PSDs of the bolometers once the common-mode is removed. These
  residual signals have significantly lower $1/f$ knees, approximately
  0.4 and 2\,Hz at 450 and 850\,\micron. Finally, the dashed black
  lines show the spectral shape produced by a point source, assuming
  that the telescope is slewing at 200\,arcsec\,sec$^{-1}$ (typical
  for S2SRO); for reference, the top horizontal axis shows the
  conversion from frequency to angular scale. We can see that the line
  features may add significant noise on the scale of the PSF. We also
  see that, for this scan velocity, the low-frequency noise begins to
  dominate on scales of approximately 8.3 and 1.7\,arcmin; these scales
  are comparable to the array footprint.}
\label{fig:pspec}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{pca.pdf}
\caption{The first six modes from a principal component analysis,
  ordered by decreasing significance, of the combined 450 and
  850\,\micron\ time-series bolometer data. For each component, the
  top plot shows the time series of the eigenvector, normalized by its
  \rms. The bottom coloured panels show the eigenvalues for the
  bolometers at each wavelength (the amplitude of the eigenvector in
  the time series). For reference, both the mean, $\bar{\lambda}$, and
  \rms, $\lambda_\mathrm{rms}$, eigenvalues for the bolometers in each
  subarray are also shown. The first two components have comparable
  amplitudes, and dominate by at least a factor of 10 any other
  components of the time series. We suspect that they are caused by
  atmospheric variations (expected to be brighter at 450\,\micron),
  and fridge oscillations (expected to be comparable at each
  wavelength). However, the two eigenvectors do not necessarily map
  directly to these physical sources under this interpretation; rather
  they are two \emph{different} linear combinations of the underlying
  physical signals that give rise to statistically uncorrelated
  components. The third component accurately reproduces an apparent
  data-acquisition glitch that appears only at 450\,\micron\ (see
  Section ???). The fourth component is a ...\,Hz line feature only
  observed in column 15 of the 450\,\micron\ subarray. The fifth
  component shows a series of steps and glitches that appear
  predominantly along the bottom-left edge of the 850\,\micron\
  subarray where the bolometers are only tenuously locked. Finally,
  the sixth component is degenerating into a less significant, and
  more randomly scattered signal across the focal plane. Subsequent
  components follow this trend, and would generally be kept in a
  PCA-cleaning procedure.}

\label{fig:pca}
\end{figure*}
